A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems

### 2014-10-30 writedown/zm/paper.water/main.tex
add new manuscript files

\documentclass[aip,jcp,a4paper,reprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}

@@

\title{A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, Japan}

>>>>

\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}

@@

\title{A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, Japan}
